%
% This is Chapter 1 file (chap1.tex)
%
\chapter{Security Evaluation}
A pentesting report for the final project of CISC472. Hosted versions of the project can be found at:

https://banningcalvin-redchan.glitch.me/

and at :

https://github.com/banningcalvin/redchan/.


\section{Trivial Vulnerabilities}
These vulnerabilities will not result in data loss, but may result in an adverse user experience. For this project, it is completely understandable that these would be present for testing purposes, but a production environment should have solutions to all of these.
\begin{itemize}
    \item Users can comment very quickly and overload a post with comments.
\end{itemize}

\section{Data Vulnerabilities}
In addition to UIDs being openly displayed, examining network output reveals even more data:

\section{Testing of other vulnerabilities}
I briefly tried a variety of common attacks to see if the application was vulnerable:
\begin{itemize}
    \item Firebase is not vulnerable to SQL injection, and it appears that all data is sent and received from firebase.
    \item Session management appears to be solid. All of this seems to be followed according to firebase specifications, and trying to break this would be a futile exercise.
\end{itemize}

\section{Vulnerability Resolution}

The most important vulnerability to patch is how posts are attributed to authors. The developers must stop attribute posts based on auth tokens, rather than a user-supplied UID. Having a Firebase function which assigns the author value in the database rather than allowing the user to pass in an arbitrary value is a quick and secure fix for this.

Next, various steps should be taken to secure this development environment before it moves to production. Identify users with a username rather than a UID, and prevent information like their personal email from being leaked by comment and post data.

Finally, spam attacks can be prevented by adding post timers or a captcha to all registrations, posts and comments, which would prevent users from creating massive volumes of phony accounts, comments, posts, and votes.